ohun: an R package for diagnosing and optimizing automatic acoustic signal detection

### 2022-08-07 manuscript/manuscript.Rmd
fabi changes

Marcelo Araya-Salas ^1,^ ^2,^ ^3^ *,
Grace Smith-Vidaurre ^4^,
Gloriana Chaverri ^3^, ^5^ 
Fabiola Chirino ^1^ &
Alejandro Rico-Guevara ^6^

>>>>

Marcelo Araya-Salas ^1,^ ^2,^ ^3^ *,
Grace Smith-Vidaurre ^4^,
Gloriana Chaverri ^3^, ^5^
Juan Carlos Brenes ^1^ &
Fabiola Chirino ^1^ &
Alejandro Rico-Guevara ^6^
